---
title: "np_leaflet"
author: "Nikolaos Perdikis"
date: "26 8 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Using Leaflet

This is a short implementation of leaflet. It shows lat/lon of points consisting a short bicycle trail in my area. The source of the data is https://www.trailforks.com/trails/prava-hrana/. This page will render the trail (via the lat/long of its vertices) on a map using leaflet. Enjoy!

```{r}
#Read file of lat,lon and add to dataframe
phrana <- "D:/Github/np_leaflet/prava-hrana.csv"
ph_trail <- read.csv(phrana,header=FALSE,sep=",",col.names=c("lat","lng"))
```

In order to create the map, we will use the data frame as the source for the lat/lon of the markers. The icon for each marker is a png from Wikipedia (that denotes the type of the trail) and also each marker is clickable to the website that contains the trail (Trailforks).  
A note on the legend of the map, is that there is no off-the-shelf implementation of icons in legends, and while solutions exist, they were considered as out-of-scope for this short demonstration. I hope you like the map and will be inspired to visit this area!

```{r}
library(leaflet)

bd_icon <- makeIcon(
    iconUrl = "https://upload.wikimedia.org/wikipedia/commons/0/0c/Ski_trail_rating_symbol-black_diamond.svg",
    iconWidth = 31*215/230, iconHeight = 31,
    iconAnchorX = 31*215/230/2, iconAnchorY = 16)

bd_site <- "<a href='https://www.trailforks.com/trails/prava-hrana/'>Prava Hrana Trail</a>"

ph_trail %>% 
    leaflet() %>%
    addTiles() %>%
    addMarkers(icon = bd_icon,popup=bd_site) %>%
    addLegend(labels = "Black Diamond", colors = c("black"))
